\section{List of Reprotool plugins}
\label{sec:plugins}

\subsection{Core model + IDE}

\begin{verbatim}
reprotool.model
\end{verbatim}
EMF model for Reprotool project, annotations and linguistic analysis attached to use case step.

\begin{verbatim}
reprotool.model.edit
\end{verbatim}
Generated Reprotool project label providers and adapter factories

\begin{verbatim}
reprotool.model.edit.ext
\end{verbatim}
Customized Reprotool project label providers and adapter factories

\begin{verbatim}
reprotool.model.editor
\end{verbatim}
Generated Reprotool project editor.

\begin{verbatim}
reprotool.model.utils
\end{verbatim}
Utility classes for EMF model manipulation.

\begin{verbatim}
reprotool.ide
\end{verbatim}
Project, Use case and Counter example editor, Reprotool project wizard, Sentence analysis view

\begin{verbatim}
reprotool.lts
\end{verbatim}
LTS EMF model

\subsection{Formal analysis}

\begin{verbatim}
reprotool.fm.nusmv
\end{verbatim}
Conversion between Reprotool project model and XText NuSMV model, parser of the
NuSMV counter example.

\begin{verbatim}
reprotool.fm.nusmv.lang
\end{verbatim}
XText NuSMV grammar definition and all runtime components (parser, lexer, linker, validation, etc.)

\begin{verbatim}
reprotool.fm.nusmv.lang.ui
\end{verbatim}
XText based NuSMV editor and all the other work-bench related functionality.

\subsection{Linguistic analysis}

\begin{verbatim}
reprotool.ling
\end{verbatim}
EMF model used for linguistic tools, linguistic analysis toolchain.

\begin{verbatim}
reprotool.ling.tests
\end{verbatim}
Tests and Benchmark of the ling. tools.

\begin{verbatim}
reprotool.tools.anna
\end{verbatim}
Wrapper plugin generated for lemmatizer.

\begin{verbatim}
reprotool.tools.dbparser
\end{verbatim}
Plugin for dbparser.jar + configuration and model (data) for Daniel Bikel's parser.

\begin{verbatim}
reprotool.tools.mxpost
\end{verbatim}
Plugin for mxpost.jar + data for MX post tagger.


\subsection{Import and export}

\begin{verbatim}
reprotool.ide.txtuc
\end{verbatim}
XText grammar definition for Textual use case editor and all runtime components (parser, lexer, linker, validation, etc.)

\begin{verbatim}
reprotool.ide.txtuc.ui
\end{verbatim}
XText based Textual use case editor and all the other work-bench related functionality.

\begin{verbatim}
reprotool.tools.txtImport
\end{verbatim}
Conversion from Textual use case to Reprotool project + wizard

\begin{verbatim}
reprotool.uml.export
\end{verbatim}
Export from Reprotool project to UML2 EMF model.

\subsection{Supporting plugins}

\begin{verbatim}
reprotool.maven.aggregator
\end{verbatim}
Maven project referencing other plugins for automated build on Jenkins CI server.

\begin{verbatim}
reprotool.maven.parent
\end{verbatim}
Common dependencies for maven projects.

\begin{verbatim}
org.eclipselabs.reprotool.branding
\end{verbatim}
Contains configuration, splashscreen and icons to style RCP application

\begin{verbatim}
org.eclipselabs.reprotool.product-plugin-based
\end{verbatim}
RCP product configuration (list of bundled plugins), needed for PDE build.

\begin{verbatim}
reprotool.exampleProjects
\end{verbatim}
Projects used in "Reprotool example projects" wizard.